---
title: "Hypothesis Testing"
author: "Santi Novani & Muhammad Apriandito"
---

```{r}
# Load packages
library(readr)
```

# Load Data
```{r}
# Load data
df_marketing <- read_csv("data/marketing.csv")
```

```{r}
# Print/Show the data
print(df_marketing)
```

# One Sample t-test (Two Sided, alpha = 0.05)
Hypothesis
H0 = the mean of Youtube adv budget is equal to 200
H1 = the mean of Youtube adv budget is not equal to 200

```{r}
# Model the t-test
ttest <- t.test(df_marketing[["youtube"]], mu = 200, alternative = "two.sided")	
```

```{r}
# Show t-test result
ttest
```

If p-value < 0.05 Reject H0
If p-value > 0.05 Accept H0

# One Sample t-test (Upper test, alpha = 0.05)

Hypothesis
H0 = the mean of Youtube adv budget is less than or equal to 200
H1 = the mean of Youtube adv budget is greater than 200

```{r}
# Model the t-test
ttest_upper <- t.test(df_marketing[["youtube"]], mu = 200, alternative = "greater")	
```

```{r}
# Show t-test result
ttest_upper
```

If p-value < 0.05 Reject H0
If p-value > 0.05 Accept H0


# One Sample t-test (Lower test, alpha = 0.05)

Hypothesis
H0 = the mean of Youtube adv budget is greater than or equal to 200
H1 = the mean of Youtube adv budget is less than 200

```{r}
# Model the t-test
ttest_lower <- t.test(df$youtube, mu = 200, alternative = "less")	
```

```{r}
# Show t-test result
ttest_lower
```

If p-value < 0.05 Reject H0
If p-value > 0.05 Accept H0

